Discrete Quantum Theories and Computing

### 2019-05-12 dissertation.tex
dissertation.lyx Acknowledgments and CV updated; Copyright Page removed...

%data for Copyright Page
\copyrightpage

@@

Except for the financial support via employment and award, I have
also supported by my family, especially my father Cheng-Tien Tai (戴振沺).
He always thinks one-step ahead and cares about my future more than
I do. Discussion with other family members and friends also helped
me to compose this dissertation, to do research, or to live better
in general, and I want to thank the following people which haven't
been listed previously:\footnote{For some of them, I only provide their Chinese names for two reason.
First, I might only know their Chinese names. Second, there are many
ways to translate a name to English, but I don't know which one they
choose.}

>>>>

%data for Copyright Page
%\copyrightpage

@@

Except for the financial support via employment and award, I have
also supported by my family, especially my father Cheng-Tien Tai (戴振沺).
He always thinks one-step ahead and cares about my future more than
I do. Discussion with other family members and friends also helped
me to compose this dissertation, to do research, or to live better
in general, and I want to thank the following people which haven't
been listed previously:\footnote{For some of them, I only provide their Chinese names for two reasons.
First, I might only know their Chinese names. Second, there are many
ways to translate a name to English, but I don't know which one they
choose.}
